\racets: Policy{-}Agnostic Programming in Racket

### 2018-07-24 paper/paper.tex
pass through paper fixing up comments and undefined refs

The rules \textsc{Box}, \textsc{Unbox}, and \textsc{Set} appear
similar to the standard implementation of boxes, but employ several
meta-functions to do their work. This is because box creation, reads,
and writes may occur within a privilaged context, and care must be
taken to form facets when \rmth{pc} is nonempty. To understand why,
consider the following example\footnote{Our formal semantics elides
  \code{if}, though it may be obtained via a Church encoding if
  desired as in Austin et al.\cite{Austin:12}. Our implementation
  includes \code{if} but not other constructs such as \code{cond}}:

@@

Last, observation evaluates the label expression to an address and
executes the associated predicate. Once this is done, \textsc{Obs}
uses the \rmth{\var{obs}} meta-function to select the appropriate
branch based on the value returned by the predicate associated with
the label. This meta-function accounts for the fact that the label
being observed may appear arbitrarily deep in the facet (or not at
all). \zw{We elide the description of the meta-function \rmth{\var{obs}}
here, but it is fully described in Austin et al.~\cite{Austin:2012}}

@@

\racets defines a \code{box} macro, along with \code{unbox} and
\code{set!}. We include the definition of \code{set!} in
Figure~\ref{fig:setbang}, which inlines the definition of the
\textit{write} metafunction from Section~\ref{sec:semantics} to
consider the case under which a facet is used when an address is
expected. \zw{The role of the \textit{write} metafunction is to 
recursively dig into faceted value, and make writes to the addresses.
If it is an address at the beginning, which hits the base case,
the \textit{write} metafunction constructs a new faceted value according
to \bmth{pc} and makes modification to the address.}

@@

Figure~\ref{fig:case} shows several screenshots of our Battleship
application. The first screenshot~\ref{fig:player1} shows the board as
viewed by player 1 (note the parameter \texttt{/player1/player1}),
while the second shows the empty board observed when player 2 attempts
to view player 1's board. The screenshot in~\ref{fig:player2strike}
shows the response seen by player 2 upon a successful hit. Finally
screenshot~\ref{fig:player1afterstrike} shows player one's board with
the ship on \bmth{(2,3)} removed.

@@

\begin{lstlisting}[language=Racket,escapechar=|,name=case]
(define p1strike
  (ext-lambda
   (request position)
   (let* ([x (char-to-num (string-ref position 0))]
          [y (char-to-num (string-ref position 2))]
          [ans (mark-hit p2board x y)]
      (set! p2board (car ans))
      (http-response
       (if (cdr (obs p2l "player2" ans)) |label{lineno:explicitobs}|
           "<h1>Congratulations!</h1> <h4>You hit player 2!</h4>"
           "<p>No hit :(</p>")))))))
\end{lstlisting}

Note that we need to use an explicit \code{obs} form on
line~\ref{lineno:explicitobs}. This is because---as \code{p2board} is
a facet---the result will also be a faceted value. When we want to
display the output to player 1, our code needs to explicitly observe
the answer, as \code{http-response} cannot accept a faceted value.

>>>>

The rules \textsc{Box}, \textsc{Unbox}, and \textsc{Set} appear
similar to the standard implementation of boxes, but employ several
meta-functions to do their work. This is because box creation, reads,
and writes may occur within a privilaged context, and care must be
taken to form facets when \rmth{pc} is nonempty. To understand why,
consider the following example\footnote{Our formal semantics elides
  \code{if}, though it may be obtained via a Church encoding if
  desired as in Austin et al.\cite{Austin:2012}. Our implementation
  includes \code{if} but not other constructs such as \code{cond}}:

@@

Last, observation evaluates the label expression to an address and
executes the associated predicate. Once this is done, \textsc{Obs}
uses the \rmth{\var{obs}} meta-function to select the appropriate
branch based on the value returned by the predicate associated with
the label. This meta-function accounts for the fact that the label
being observed may appear arbitrarily deep in the facet (or not at
all). As our implementation of \rmth{\var{obs}} is unchanged from its
definition in~\cite{Austin:2012}, we elide it here.

@@

\racets defines a \code{box} macro, along with \code{unbox} and
\code{set!}. We include the definition of \code{set!} in
Figure~\ref{fig:setbang}, which inlines the definition of the
\textit{write} metafunction from Section~\ref{sec:semantics} to
consider the case under which a facet is used when an address is
expected.

@@

Figure~\ref{fig:case} shows several screenshots of our Battleship
application. The first screenshot~\ref{fig:player1} shows the board as
viewed by player 1 (using the route \texttt{/player1/player1}),
while the second shows the empty board observed when player 2 attempts
to view player 1's board. The screenshot in~\ref{fig:player2strike}
shows the response seen by player 2 upon a successful hit. Finally
screenshot~\ref{fig:player1afterstrike} shows player one's board with
the ship on \bmth{(2,3)} removed.

@@

\begin{lstlisting}[language=Racket,escapechar=|,name=case]
(define p1strike
  (ext-lambda
   (request position)
   (let* ([x (char-to-num (string-ref position 0))]
          [y (char-to-num (string-ref position 2))]
          [ans (mark-hit p2board x y)]
      (set! p2board (car ans))
      (http-response
       (if (cdr (obs p2l "player2" ans))
           "<h1>Congratulations!</h1> <h4>You hit player 2!</h4>"
           "<p>No hit :(</p>")))))))
\end{lstlisting}

Note that we need to use an explicit \code{obs} form on
line 25. This is because---as \code{p2board} is
a facet---the result will also be a faceted value. When we want to
display the output to player 1, our code needs to explicitly observe
the answer, as \code{http-response} cannot accept a faceted value.
